---
title: "paisaje: landscape analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{paisaje: landscape anlysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The goal of **paisaje** is to provide tools for spatial and landscape analysis in R.  It includes functions for working with landscape metrics, spatial data manipulation, and biodiversity conservation applications.

## Installation

You can install the development version of paisaje from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("ManuelSpinola/paisaje")
```

## Example

This is a basic example which shows you how to use the package:

```{r}
#| message: false
#| warning: false
library(paisaje)
library(ggplot2)
library(sf)
library(h3jsr)
```

Let's bring an sf object

```{r}
#| message: false
#| warning: false
nc = st_read(system.file("shape/nc.shp", package="sf"))
```

Create an h3 grid of resolution 4

```{r}
#| message: false
#| warning: false
h3_grid_nc <- get_h3_grid(nc, resolution = 4)
```

Make a map

```{r}
ggplot() +
  theme_minimal() +
  geom_sf(data = nc, color = "blue", linewidth = 0.5) +
  geom_sf(data = h3_grid_nc, alpha = 0.4, color = "coral", linewidth = 0.5)
```

